Summary Tables

### 2022-11-29 summary_tables.Rmd
Comment code to create health outcomes as an excel sheet

# Remove CIs
ylls <-  rbindlist(health$ylls$hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
ylls_pathway <- rbindlist(health$ylls$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths <- rbindlist(health$deaths$hb, use.names = T)|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths_pathway <- rbindlist(health$deaths$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))

# Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls = ylls,
                         ylls_pathway = ylls_pathway,
                         deaths = deaths,
                         deaths_pathway = deaths_pathway), 
                    path = output_file)

>>>>

# Remove CIs
ylls <-  rbindlist(health$ylls$hb, use.names = T) #|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
ylls_pathway <- rbindlist(health$ylls$pathway_hb, use.names = T) #|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths <- rbindlist(health$deaths$hb, use.names = T) #|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths_pathway <- rbindlist(health$deaths$pathway_hb, use.names = T) #|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))

# # Export ylls HB
# output_file <- "results/multi_city/health_impacts/data.xlsx"
# writexl::write_xlsx(list(ylls = ylls,
#                          ylls_pathway = ylls_pathway,
#                          deaths = deaths,
#                          deaths_pathway = deaths_pathway), 
#                     path = output_file)
